Dynamics Analysis: The Sound of Teaching Music 2

### 2022-06-27 experiment-2/analysis/stats/dynamics.Rmd
update additional analysis
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

```{r vel-diff-art, echo = FALSE}
# For each individual
vel_diff_art <- dt_vel_diff_art[Subcomponent == "LtoS" | Subcomponent == "StoL", .(N = .N, Mean = mean(Diff), SD = sd(Diff)), by = .(SubNr, Condition, Skill, Subcomponent)]
vel_diff_art
```

### Plot
#### Box plot
```{r vel-diff-art-box,  echo = FALSE}
ggboxplot(dt_vel_diff_art[Subcomponent == "LtoS" | Subcomponent == "StoL", .(N = .N, Mean = mean(Diff), SD = sd(Diff)), by = .(SubNr, Condition, Skill, Subcomponent, BlockNr, TrialNr)], "SubNr", "Mean", color = "Condition", xlab = "SubNr", ylab = "Difference", title = "KV-Diff: Articulation") +
  facet_grid(Subcomponent ~ .)
```

@@

```{r vel-diff-art-trial, echo = FALSE}
# For each individual
vel_diff_art_trial <- dt_vel_diff_art[Subcomponent == "LtoS" | Subcomponent == "StoL", .(N = .N, Mean = mean(Diff), SD = sd(Diff)), by = .(SubNr, Condition, Skill, Subcomponent, TrialNr)]
vel_diff_art_trial
```

>>>>

```{r vel-diff-art, echo = FALSE}
# For each individual
vel_diff_art_trial <- dt_vel_diff_art[Subcomponent == "LtoS" | Subcomponent == "StoL", .(N = .N, Mean = mean(Diff), SD = sd(Diff)), by = .(SubNr, Condition, Skill, BlockNr, TrialNr, Subcomponent)]

vel_diff_art <- vel_diff_art_trial[, .(N = .N, Mean = mean(Mean), SD = sd(Mean)), by = .(SubNr, Condition, Skill, Subcomponent)]
vel_diff_art
```

### Plot
#### Box plot
```{r vel-diff-art-box,  echo = FALSE}
ggboxplot(vel_diff_art_trial[, .(N = .N, Mean = mean(Mean), SD = sd(Mean)), by = .(SubNr, Condition, Skill, Subcomponent, BlockNr, TrialNr)], "SubNr", "Mean", color = "Condition", xlab = "SubNr", ylab = "Difference", title = "KV-Diff: Articulation") +
  facet_grid(Subcomponent ~ .)
```

@@

```{r vel-diff-art-trial, echo = FALSE}
# For each individual
vel_diff_art_trial
```
